The Practical Application of Computerised Multistage Tests

### 2021-02-24 article.Rmd
Use png images (not svg)

---
title: "The Practical Application of Computerised Multistage Tests"
author:
- name: James Page
  affiliation: SP Educational Consulting
  affiliation_url: https://www.speduconsulting.co.uk/
date: "`r Sys.Date()`"
output:
  pdf_document:
    toc: true
    toc_depth: 2
    highlight: haddock
    latex_engine: lualatex
  word_document: default
  html_document: default
version: 1
description: |
  A practical guide to the design and development of computerised multistage tests.
bibliography: references.bib
---

@@

![Logistic Function](images/icc.png)

@@

![Logistic Function](images/iif.png)

@@

![MST Design](images/modules.svg)

@@

![Panels](images/panels.svg)

@@

![MST Design](images/module-items.svg)

@@

![Module A Items](images/moduleA-items.svg)
A group of raters will be used to validate items in a level panel exercise, and ensure that they are set at the correct target difficulty level. Rating sheets are then collated and a decision then made on the CEFR rating for each item in the item bank. Various methods can be used to converge on an agreed difficulty level for each item; the simplest is to find the modal (ie. the most frequently occurring) from all your raters. Where there is no single mode, or there are wide disagreements between raters, a manual adjustment to a commonly agreed difficulty level that is close to the average may be required. Ideally at least 5 raters would be used for each item to avoid this as far as possible.

>>>>

---
title: "The Practical Application of Computerised Multistage Tests"
author:
- name: James Page
  affiliation: SP Educational Consulting
  affiliation_url: https://www.speduconsulting.co.uk/
date: "`r Sys.Date()`"
output:
  pdf_document:
    toc: true
    highlight: pygments
    latex_engine: lualatex
    fig_width: 5
version: 1
description: |
  A practical guide to the design and development of computerised multistage tests.
bibliography: references.bib
---

@@

![Item Characteristic Curves](images/icc.png)

@@

![Item Information Functions](images/iif.png)

@@

![MST Design](images/modules.png)

@@

![Panels](images/panels.png)

@@

![MST Design](images/module-items.png)

@@

![Module A Items](images/moduleA-items.png)
A group of raters will be used to validate items in a level panel exercise, and ensure that they are set at the correct target difficulty level. Rating sheets are then collated and a decision then made on the CEFR rating for each item in the item bank. Various methods can be used to converge on an agreed difficulty level for each item; the simplest is to find the modal (ie. the most frequently occurring) from all your raters. Where there is no single mode, or there are wide disagreements between raters, a manual adjustment to a commonly agreed difficulty level that is close to the average may be required. Ideally at least 5 raters would be used for each item to avoid this as far as possible.
